ComparativePlots

### 2019-07-19 ComparativePlots.Rmd
Changes after Devis comments

```{r}
cols <- c("#543005", "#8c510a", "#bf812d", "#dfc27d", "#c0d884",
           brewer.pal(n = 9, name = "BuGn")[4:9])
cols <- c('#B76643','#B76643','#B76643','#B76643','#B47339','#AC8032','#A08E33','#909B3C','#7DA64D', brewer.pal(n = 9, name = "Greens")[5:9], "#00441B", "#00441B", "#00441B")

cols <- c("#543005", "#8c510a", "#bf812d", "#dfc27d", "#c0d884",
           brewer.pal(n = 9, name = "YlGn")[4:9])

cols <- c(
'#543005',
'#8c510a',
'#fd8d3c',
'#feb24c',
'#fed976',
'#ffeda0',
#'#f7fcb9',
'#d9f0a3',
'#addd8e',
'#78c679',
'#41ab5d',
'#238443',
'#006837',
'#006837',
'#004529',
'#004529',
'#004529')

cols <- c(
'#211F29',
'#262B37',
'#2A3945',
'#2C4751',
'#2D565C',
'#2F6565',
'#34746C',
'#3E8470',
'#4D9371',
'#60A171',
'#78B06F',
'#92BD6D',
'#B0C96B',
'#D0D46B'
)

restricted.data %>% ggplot(aes(x = exp(MCC.DR), y = 0, fill = ..x..))+
  geom_density_ridges_gradient(scale = 3, size = 0.05, gradient_lwd = 0.75)+
  scale_fill_gradientn(colours = cols, guide = F, breaks = c(0.02, 0.1, 0.5, 2.5))+
  theme_minimal()+
  scale_x_continuous(trans = "log", breaks = c(0.02, 0.1, 0.5, 2.5))+
  scale_y_discrete(expand = c(0,0))+
  theme(axis.text.y = element_blank(),
        axis.title.y = element_blank(),
        axis.text.x = element_text(size = 14),
        axis.line.y = element_blank(), 
        panel.grid = element_blank(),
        axis.title.x = element_blank(),
        axis.ticks.x.bottom = element_line())

@@

```{r}
cols <- c("#543005", "#8c510a", "#bf812d", "#dfc27d", "#d9ef8b",
           brewer.pal(n = 9, name = "YlGn")[4:9])
display.brewer.pal(n = 11, name = "RdYlGn")[4:11]
#cols <- c("#045a8d", "#74a9cf", "#ffd92f", "#d9f0a3", "#78c679", "#005a32")
#20 x 20 plots
ggtree.plot.dr <- ggtree(fortified.DR.tree, aes(color =  rate),
                      layout="fan", open.angle = 90, size = 0.175) + 
  xlim(-75, NA)+
  scale_color_distiller(palette = "YlGn", direction = 1, guide = F, trans = "log", breaks=c(0.05, 0.15, 0.5, 1.5))+
  theme(legend.position = "bottom",
        legend.text = element_text(size = 18))

>>>>

```{r}
cols <- c("#543005", "#8c510a", "#bf812d", "#dfc27d", "#c0d884",
           brewer.pal(n = 9, name = "YlGn")[4:9])
cols <- c('#B76643','#B76643','#B76643','#B76643','#B47339','#AC8032','#A08E33','#909B3C','#7DA64D', brewer.pal(n = 9, name = "Greens")[5:9], "#00441B", "#00441B", "#00441B")

cols <- c("#543005", "#8c510a", "#bf812d", "#dfc27d", "#c0d884",
           brewer.pal(n = 9, name = "YlGn")[4:9])
# 
# cols <- c(
# '#543005',
# '#8c510a',
# '#fd8d3c',
# '#feb24c',
# '#fed976',
# '#ffeda0',
# #'#f7fcb9',
# '#d9f0a3',
# '#addd8e',
# '#78c679',
# '#41ab5d',
# '#238443',
# '#006837',
# '#006837',
# '#004529',
# '#004529',
# '#004529')
# 
# cols <- c(
# '#211F29',
# '#262B37',
# '#2A3945',
# '#2C4751',
# '#2D565C',
# '#2F6565',
# '#34746C',
# '#3E8470',
# '#4D9371',
# '#60A171',
# '#78B06F',
# '#92BD6D',
# '#B0C96B',
# '#D0D46B'
# )

restricted.data %>% ggplot(aes(x = exp(MCC.DR), y = 0, fill = ..x..))+
  geom_density_ridges_gradient(scale = 3, size = 0.05, gradient_lwd = 0.75)+
  scale_fill_distiller(palette = "YlGn", direction = 1, labels = )+
  theme_minimal()+
  scale_x_continuous(breaks = c(0.02, 0.1, 0.5, 2.5), trans = "log")+
  scale_y_discrete(expand = c(0,0))+
  theme(axis.text.y = element_blank(),
        legend.direction = "horizontal",
        legend.position = "bottom",
        axis.title.y = element_blank(),
        axis.text.x = element_text(size = 14),
        axis.line.y = element_blank(), 
        panel.grid = element_blank(),
        axis.title.x = element_blank(),
        axis.ticks.x.bottom = element_line())

@@

```{r}
cols <- c("#543005", "#8c510a", "#bf812d", "#dfc27d", "#d9ef8b",
           brewer.pal(n = 9, name = "YlGn")[4:9])
display.brewer.pal(n = 11, name = "RdYlGn")[4:11]
#cols <- c("#045a8d", "#74a9cf", "#ffd92f", "#d9f0a3", "#78c679", "#005a32")
#20 x 20 plots
ggtree.plot.dr <- ggtree(fortified.DR.tree, aes(color =  rate),
                      layout="fan", open.angle = 90, size = 0.175) + 
  xlim(-75, NA)+
  scale_color_distiller(palette = "YlGn", direction = 1, trans = "log", breaks=c(0.05, 0.15, 0.5, 1.5))+
  theme(legend.position = "bottom",
        legend.text = element_text(size = 18))
